---
title: "Deep Knowledge Tracing"
author: "Larry Liu"
date: "February 5, 2016"
output: html_document
---

Notes:
Currently running on hoc2

---

This block initializes libraries necessary for the script.
```{r, echo=FALSE}
library('ggplot2')
library('animation')
library('stringr')

#Change working directory
setwd("C:/Users/Larry/Dropbox/Stanford University/2015-2016/Winter Quarter/CS191W/deepcode")

```

This block reads in AST count data and score data, determines the correctness of each AST, and plots them.
```{r}
#Import count data
astCounts <- as.data.frame(read.table("C:/Users/Larry/Dropbox/Stanford University/2015-2016/Winter Quarter/CS191W/hoc1-9_new/hoc2/asts/counts.txt", sep="\t", header=FALSE))
colnames(astCounts) = c('astID', 'count')

#Import score data
astScores <- as.data.frame(read.table("C:/Users/Larry/Dropbox/Stanford University/2015-2016/Winter Quarter/CS191W/hoc1-9_new/hoc2/asts/unitTestResults.txt", sep="\t", header=FALSE))
colnames(astScores) = c('astID', 'score')

#Determine correctness of scores
astScores['correct'] = ifelse(astScores['score'] == 100 | astScores['score'] == 20, 1, 0)

astHist = ggplot(data=astCounts, aes(x=astID, y=count)) + geom_bar(stat='identity') + labs(title="AST frequency", x="AST ID", y="Frequency") + scale_y_log10() + scale_x_continuous()
astHist

astHist2 = ggplot(data=astCounts[astCounts$count > 1,], aes(x=astID, y=count)) + geom_bar(stat='identity') + labs(title="AST frequency", x="AST ID", y="Frequency") + scale_y_log10() + scale_x_continuous()
astHist2


astScorePlot = ggplot(data=astScores, aes(x=astID, y=score, colour=as.factor(correct))) + geom_point() + labs(title="AST Scores", x="AST ID", y="Score") + scale_y_continuous(breaks=seq(0,100,10), limits=c(0,100)) + scale_x_continuous() + scale_color_manual(values=c("red", "green"))
astScorePlot

```

This block processes and plots all trajectory frequencies.
```{r}
trajCounts <- as.data.frame(read.table("C:/Users/Larry/Dropbox/Stanford University/2015-2016/Winter Quarter/CS191W/hoc1-9_new/hoc2/trajectories/counts.txt", sep="\t", header=FALSE))
colnames(trajCounts) = c('trajID', 'count')

trajHist = ggplot(data=trajCounts, aes(x=trajID, y=count)) + geom_bar(stat='identity') + labs(title="Trajectory frequency", x="Trajectory ID", y="Frequency") + scale_y_log10() + scale_x_continuous()
trajHist

#Remove all trajectory IDs with count 1
trajHist2 = ggplot(data=trajCounts[trajCounts$count > 1,], aes(x=trajID, y=count)) + geom_bar(stat='identity') + labs(title="Trajectory frequency", x="Trajectory ID", y="Frequency") + scale_y_log10() + scale_x_continuous()
trajHist2 

```


This block processes all trajectories' last AST and the associated score.
```{r}
#setwd("C:/Users/Larry/Dropbox/Stanford University/2015-2016/Winter Quarter/CS191W/hoc1-9_new/hoc2")
filenameBase = "'C:/Users/Larry/Dropbox/Stanford University/2015-2016/Winter Quarter/CS191W/hoc1-9_new/hoc2/trajectories/"

numTrajs = 100

#Create data frame to store trajectory data
trajData = data.frame(matrix(NA, nrow=numTrajs, ncol=3))
colnames(trajData) = c('trajID', 'lastAST', 'score')

for(trajID in 0:numTrajs){
  #File name of the trajectory to open
  filename = paste(filenameBase, trajID, ".txt'", sep="")
  
  #Retrieve the last AST in a given trajectory
  lastAST <- as.numeric(system(paste("gawk 'END {print}'", filename, sep=" "), intern = TRUE))
  
  #Store last AST and score coupled with trajID
  trajData[trajID+1,] = c(trajID, lastAST, astScores[astScores$astID == lastAST,]$score)
}

#Determine correctness of scores
trajData['correct'] = ifelse(trajData['score'] == 100 | trajData['score'] == 20, 1, 0)

trajScorePlot = ggplot(data=trajData, aes(x=trajID, y=score, colour=as.factor(correct))) + geom_point() + labs(title="Trajectory Scores", x="Traj ID", y="Score") + scale_y_continuous(breaks=seq(0,100,10), limits=c(0,100)) + scale_x_continuous() + scale_color_manual(values=c("red", "green"))
trajScorePlot
```

This block computes the score for each student given their trajectory.
```{r}
studentTrajs <- as.data.frame(read.table("C:/Users/Larry/Dropbox/Stanford University/2015-2016/Winter Quarter/CS191W/hoc1-9_new/hoc2/trajectories/idMap.txt", sep=",", header=FALSE))
colnames(studentTrajs) = c('studentID', 'trajID')

#Add score column
for(studentID in studentTrajs[1:10000,]$studentID){
  currTrajID = studentTrajs[studentTrajs$studentID == studentID,]$trajID
  if(currTrajID < numTrajs){
    
    #index into 1-indexed trajectory data frame
    studentTrajs[studentTrajs$studentID == studentID,3] = trajData[currTrajID+1,]$score
  }
}

colnames(studentTrajs) = c('studentID', 'trajID', 'score')
```

This block computes the grade distribution.
```{r}
grades = data.frame(score=numeric(0), count=numeric(0))
for(i in 0:numTrajs){
  currScore = trajData[i+1,]$score
  currCount = trajCounts[i+1,]$count
  if(is.na(grades[currScore,]$count)){
    grades[currScore,] = c(currScore, currCount)
  }
  else{
    grades[currScore,2] = grades[currScore,2] + currCount
  }
}

grades = grades[complete.cases(grades),]

gradesHist = ggplot(data=grades, aes(x=score, y=count)) + geom_bar(stat='identity') + labs(title="Grade Distribution", x="Score", y="Frequency") + scale_y_log10() + scale_x_continuous()
gradesHist

totalScore = sum(grades$score * grades$count)
totalCounts = sum(grades$count)
correctCounts = sum(grades[grades$score >= 20,]$count)
meanGrade = totalScore/totalCounts
percentCorrect = correctCounts/totalCounts
percentGold = grades[grades$score == 100,]$count/totalCounts
grades$meandiffSquared = (grades$score - meanGrade)^2
variance = sum(grades$meandiffSquared * grades$count)/totalCounts
stdev = variance ^ 0.5

summary(grades)
print(paste("Min grade:", min(grades$score)))
print(paste("Max grade:", max(grades$score)))
#print(paste("Median grade:", ifelse(grades['score'] == 100 | astScores['score'] == 20, 1, 0)))
print(paste("Mean grade:", meanGrade))
print(paste("Variance:", variance))
print(paste("St.Dev:", stdev))

print(paste("Percentage correct: ", percentCorrect))
print(paste("Percentage gold: ", percentGold))
```
```{r}
#Change working directory
setwd("C:/Users/Larry/Dropbox/Stanford University/2015-2016/Winter Quarter/CS191W/hoc1-9_new/hoc2/trajectories")

filelist = list.files(pattern="^[[:digit:]]*.txt")
```